\documentclass[12pt]{scrartcl}

% Packages
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[dvipsnames]{xcolor}
\usepackage{spectral}
\usepackage[T1]{fontenc}
\usepackage{accsupp}

% Font
\setkomafont{disposition}{\normalfont\bfseries}

% Readability
\input{glyphtounicode}
\pdfgentounicode=1

% Layout Configurations
\geometry{margin=0.75in}
\setcounter{secnumdepth}{0}
\pagestyle{empty}

% Some Commands
\newcommand{\hll}[1]{{\color{RawSienna}#1}}
\newcommand{\hlp}[1]{{\color{Maroon}#1}}

% Document
\begin{document}

\begin{center}
	\begin{tabular}{rl}
		\huge Prasanth Thomas & \huge Shaji \\
		[0.42em]
		\small {\color{blue}\faIcon{linkedin}} \href{https://www.linkedin.com/in/prasanth-thomas-shaji/}{Prasanth Shaji} & \small {\color{black}\faIcon{github}} \href{https://github.com/paperbound}{paperbound} \\
		\small \href{mailto:prasanthshaji@icloud.com}{prasanthshaji@icloud.com} & \small \href{tel:+46764524046}{+46 76 452 40 46}
	\end{tabular}
\end{center}

\vspace{2em}

Experienced in distributed systems, application programming, computer architecture, and embedded systems. Passionate about building lasting software.

\vspace{1em}

\noindent \textbf{Skills} \hll{C}, \hll{C++}, \hll{Rust}, \hll{Python}, \hll{Golang}, \hll{Java}, \hlp{UNIX}, \hlp{Bash}, \hlp{Emacs}, \hlp{VS Code}, \hlp{Docker} (Container), \hlp{Puppet} (IaC / Orchestration), \hlp{PyTorch} (ML/ANN frameworks), \hlp{Kafka}, \hlp{Git}, \hlp{Gerrit}, \hlp{JIRA}, Agile

\section{Experience}

\subsection[Scania]{Scania \hfill September 2022 - April 2023}

\subsubsection{Master's Thesis Worker}

Reverse engineering Linux environments on i.MX6 based ECU, benchmarking Neural Network training in Embedded Platforms

\subsection[Affle]{Affle \hfill September 2018 - February 2020}

\subsubsection{Software Engineer}

After Vizury AdServing was acquired by Affle Pvt Ltd., migrated then maintained the AdTech platform in a 4-person team, set up \hlp{DevOps} best practises.

\subsection[Vizury]{Vizury \hfill July 2017 - August 2018}

\subsubsection{Software Engineer}

Software Developer for Vizury AdServing, and \textit{lemnisk}'s FinTech CDP app. Migrated \hll{Java} apps across \textit{cloud service providers (IBM SoftLayer to AWS)}.

\section{Education}

\subsection[Uppsala Universitet]{Uppsala University, Sweden \hfill August 2021 - August 2023}

\subsubsection{Master of Science in Computer Science \hfill {\color{lightgray} 4.71/ 5}}

Focused on Embedded Systems, Computer Architecture, and Performance Engineering.

\subsection[NITC]{NIT Calicut, India \hfill July 2013 - June 2017}

\subsubsection{Bachelor of Technology in Computer Science \& Engineering \hfill {\color{lightgray} 7.85/ 10}}

Embraced Computational Thinking and Mastered Foundations of Computer Science.

\section{Projects}

\subsubsection[Benchmarking ANNs]{\href{https://github.com/paperbound/hdrnn-arm}{Training Neural Networks on Embedded Devices} \hfill Masters Thesis @ Scania}

Implemented programs to benchmark neural network training in \hll{C} / \hll{C++} / \hll{Python} / \hlp{PyTorch}. Completed benchmarking on \hlp{ARM} boards \& through \hlp{QEMU} emulation.

\subsubsection[Argo DSM]{Prefetch Strategies for Argo Distributed Shared Memory System \hfill Uppsala University}

\href{https://github.com/etascale/argodsm}{ArgoDSM} is a software distributed shared memory system written in \hll{C++}. Implemented stride based prefetching of the DSM pages within ArgoDSM and analysed application performance.

\subsubsection[Xilinx FPGA NN Inference]{Neural Network inference on Xilinx based FPGA \hfill Uppsala University}

Implemented Neural Network inference for handwritten digit recognition on Avnet MiniZed. Used the \hlp{Zynq 7Z007S} logic elements (FPGA) on the MiniZed using Xilinx \hlp{Vivado}.

\subsubsection[WCNES NRF51]{Evaluated RPL+TSCH Network Performance using nRF51 DK \hfill Uppsala University}

Used TSCH and 6TiSCH capabilities of Contiki-NG operating system to test file transfer speeds using multiple nRF51 DK boards.

\subsubsection[Kafka Migration]{Migrating Kafka Data Pipeline from across AWS accounts \hfill Affle}

Completed the data pipeline ownership handover from Vizury to Affle. Migrated high volume event bus from one \hlp{Kafka} system to another without disrupting services.

% \subsubsection[ML in RTB]{Neural Network based OpenRTB Bid Calculations \hfill Vizury}

% Developed and tested integrations for \hlp{Tensorflow} based DNN model inferences for a Real Time Bidding Engine.

% \subsubsection[AdServing codebase migrations]{Completed Migration of an Ad Server codebase from \hll{PhP} to \hll{Java} \hlp{Springboot} \hfill Vizury}

% Completed codebase migrations from \hll{PhP} to \hll{Java} \hlp{Spring Boot} for an Ad Serving application. Set up \textit{DevOps \hlp{CI/CD}} components such as orchestration through \hlp{puppet}.

\subsubsection[sDHT]{Secure Distributed Hash Tables \hfill B.Tech Project @ NITC}

Implemented a \textit{distributed hash table} in \hll{Golang} using \hlp{Raft} as the \textit{consensus protocol} and a \textit{sybil attack} resistant cryptographic scheme.

\end{document}
